\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-15 article.tex
some wording about H-P filter

The raw signal is the calcium fluorescence imaging representing neuron activity. Considering the imaging process, we have to cope with a slower sampling rate than the neuron firing frequency and the slow decay of fluorescent calcium indicator after a neuron activity burst.

@@

Prior inferring the network, the fluorescent calcium time series
are smoothed using several linear and non linear filters.
Considering the short delay for a communication between neurons, slow events
can be neglected to retrieve direct relationships. The average time
delay is indeed about $1ms$ or $2ms$ while the fluorescent signal time
resolution is $20ms$. Let us also highlight that even if two neurons are
spatially far from each other, the information is expected in the same time
step or at most in the next time step. Thus very low frequency event can be neglected.
However, the image fluorescence calcium signal is also very noisy. Thus,
A low-pass filter (Equation \ref{eq:low-pass}) is first applied followed by a
high-pass filter (Equation \ref{eq:high-pass}), the discrete derivative of
the signal,
\begin{align}
X^\prime_{t,i} &= \sum_{l=-3}^2 c_l^k X_{t+l,i} \forall i, \label{eq:low-pass}\\
X^{\prime\prime}_{t,i} &= X^{\prime}_{t,i} - X^{\prime}_{t-1,i} \forall i, \label{eq:high-pass}
\end{align}
where the $c_l^k$ coefficients were taken in one of the four
following tuples
$\left(c_l^1\right)_{l=-3}^2=(0, 0, 1, 1, 1, 1)$,
$\left(c_l^2\right)_{l=-3}^2=(0, 0, 1, 1, 1, 0)$,
$\left(c_l^3\right)_{l=-3}^2=(1, 1, 1, 1, 0, 0)$ or
$\left(c_l^4\right)_{l=-3}^2=(0.4, 0.8, 1, 1, 0, 0)$.

>>>>

\textcolor{red}{The raw signal is the calcium fluorescence imaging representing neuron activity. Considering the imaging process, we have to cope with a slower sampling rate than the neuron firing frequency and the slow decay of fluorescent calcium indicator after a neuron activity burst.}

@@

Prior inferring the network, the fluorescent calcium time series
are smoothed using several linear and non linear filters \textcolor{red}{in order to reduce the imaging process effects. We successively apply different filters listed below.} \\

% However, the image fluorescence calcium signal is also very noisy. Thus,
% A low-pass filter (Equation \ref{eq:low-pass}) is first applied followed by a
% high-pass filter (Equation \ref{eq:high-pass}), the discrete derivative of
% the signal,
% \begin{align}
% X^\prime_{t,i} &= \sum_{l=-3}^2 c_l^k X_{t+l,i} \forall i, \label{eq:low-pass}\\
% X^{\prime\prime}_{t,i} &= X^{\prime}_{t,i} - X^{\prime}_{t-1,i} \forall i, \label{eq:high-pass}
% \end{align}
% where the $c_l^k$ coefficients were taken in one of the four
% following tuples
% $\left(c_l^1\right)_{l=-3}^2=(0, 0, 1, 1, 1, 1)$,
% $\left(c_l^2\right)_{l=-3}^2=(0, 0, 1, 1, 1, 0)$,
% $\left(c_l^3\right)_{l=-3}^2=(1, 1, 1, 1, 0, 0)$ or
% $\left(c_l^4\right)_{l=-3}^2=(0.4, 0.8, 1, 1, 0, 0)$.

\textcolor{red}{As it can be seen on \textit{fig 1}, the raw signal is very noisy and a low-pass filter is therefore applied to get a cleaner version of the signal where only true variations are kept, i.e. without noise variations. However, the choice of a low-pass filter is not unique. In the rest of the paper, we will focus on two types, the symmetrical median filter, i.e., $X_t^i \leftarrow X_{t-1}^i + X_{t}^i + X_{t+1}^i$, and an asymmetrical weighted median filter, i.e., $X_t^i \leftarrow 0.4 X_{t-3}^i + 0.6 X_{t-2}^i + 0.8 X_{t-1}^i + X_{t}^i$.}

\textcolor{red}{Considering the short delay for a communication between neurons, slow events can be neglected to retrieve direct relationships. Indeed, for a direct relationship, i.e. a neuron firing directly implying another neuron to fire, the average time is about $1ms$ or $2ms$ while the fluorescent signal time resolution is $20ms$. In order to find out which neurons are directly related, it is only necessary to look after the burst signal, or in other words, wether there is a signal variable, i.e. a burst.}

% Considering the short delay for a communication between neurons, slow events
% can be neglected to retrieve direct relationships. The average time
% delay is indeed about $1ms$ or $2ms$ while the fluorescent signal time
% resolution is $20ms$. Let us also highlight that even if two neurons are
% spatially far from each other, the delay should not exceed one time step. Thus very low frequency event can be neglected.
